---
title: "3soils_markdown"
author: "Kaizad Patel"
output: word_document
---

This is the RMarkdown file for the 3Soils experiment. Tables and figures for molecular results.
For formatted tables, see the Word document titled `000-3soils_markdown_YYYYMMDD.docx`.

Run: `r Sys.Date()`


```{r setup, include=FALSE, echo=FALSE}
source("0-packages.R")

# input files
#   CHARAC
charac = read.csv(CHARACTERIZATION)# <- "processed/soil_characterization.csv"
pore = read.csv(PORE_DISTRIBUTION)# <- "processed/pore_distribution.csv"

# WSOC
wsoc_pore = read.csv(WSOC_PORE)# <- "processed/wsoc_pore_summary.csv"
wsoc_soil = read.csv(WSOC_SOIL)# <- "processed/wsoc_soils_summary.csv"

# FTICR -- longform files
soil_raw = read.csv(FTICR_SOIL_RAW_LONG)# <- "fticr/fticr_soil_raw_longform.csv"
soil_long = read.csv(FTICR_SOIL_LONG)# <- "fticr/fticr_soil_longform.csv"
pore_long = read.csv(FTICR_PORE_LONG)# <- "fticr/fticr_pore_longform.csv"
pore_raw = read.csv(FTICR_PORE_RAW_LONG)# <- "fticr/fticr_pore_raw_longform.csv"

# FTICR -- relative abundance files
pore_relabund = read.csv(FTICR_PORE_RELABUND)# <- "fticr/fticr_pore_relabundance_groups2_hsd.csv"
soil_relabund = read.csv(FTICR_SOIL_RELABUND)# <- "fticr/fticr_soil_relabundance_hsd.csv"

# FTICR -- peaks files
pore_unique = read.csv(FTICR_PORE_UNIQUE)# <- "fticr/fticr_pore_uniquemolecules.csv"
soil_unique = read.csv(FTICR_SOIL_UNIQUE)# <- "fticr/fticr_soil_uniquemolecules.csv" 

pore_peaks = read.csv(FTICR_PORE_PEAKS)# <- "fticr/fticr_pore_peakscount.csv"
soil_peaks = read.csv(FTICR_SOIL_PEAKS)# <- "fticr/fticr_soil_peakscount.csv"


# FTICR_PORE
pore_aromatic = read.csv(FTICR_PORE_AROMATIC)# <- "fticr/fticr_pore_aromatic_counts.csv"
pore_meta = read.csv(FTICR_PORE_META)# <- "fticr/fticr_pore_meta.csv"
pore_long = read.csv(FTICR_PORE_LONG)# <- "fticr/fticr_pore_longform.csv"
pore_unique_peaks = read.csv(FTICR_PORE_UNIQUE_PEAKS)# <- "fticr/fticr_pore_unique_peakscount.csv"
pore_hcoc = read.csv(FTICR_PORE_HCOC)# <- "fticr/fticr_pore_hcoc.csv"
pore_nosc = read.csv(FTICR_PORE_NOSC)# <- "fticr/fticr_pore_nosc.csv"
pore_shannon = read.csv(FTICR_PORE_DIVERSITY)# <- "fticr/fticr_pore_shannondiversity.csv"

  
  
#FTICR_SOIL
soil_aromatic = read.csv(FTICR_SOIL_AROMATIC)# <- "fticr/fticr_soil_aromatic_counts.csv"
soil_nosc = read.csv(FTICR_SOIL_NOSC)# <- "fticr/fticr_soil_nosc.csv"
soil_hcoc = read.csv(FTICR_SOIL_HCOC)# <- "fticr/fticr_soil_hcoc.csv"
soil_unique_peaks = read.csv(FTICR_SOIL_UNIQUE_PEAKS)# <- "fticr/fticr_soil_unique_peakscount.csv"


```
# Soil characterization
## summary table
```{r charac, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="relabund 50 kPa"}
charac %>% 
  dplyr::mutate(variable = factor(variable, levels = c("TC_perc", "TN_perc", "TOC_perc", "WSOC_mg_g",
                                                "Ca_meq100g", "Mg_meq100g",
                                                "pH", "EC_dS_m", 
                                                "Sand_perc", "Silt_perc", "Clay_perc"))) %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(site),
                val = paste(summary_hsd)) %>% 
  dplyr::select(variable,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```
---
## pore distribution
```{r pores, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="pore size distribution",fig.path = "images/"}
 ggplot(pore,aes(x = pore_size, y=freq,color = site))+
  geom_line(size = 1)+
  scale_color_brewer(palette = "Set2")+
  #geom_density(adjust=0.5)+
  
  labs (y = expression (bold ("distribution, %"),
                        x = expression (bold ("pore size" ))))+
  theme_bw()+
  theme_kp()

```
---
## water retention curves

```{r wrc, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="water retention curve", fig.width=5, fig.height=5,,fig.path = "images/"}

water_retention = read_excel("data/water_retention.xlsx")

# van genuchten plots
ggplot()+
  geom_line(data = water_retention,aes(x = Tension_c, y = CPCRW_water_VG, color = "CPCRW"), size=1)+
  geom_line(data = water_retention,aes(x = Tension_d, y = DWP_water_VG,color = "DWP"), size=1)+
  geom_line(data = water_retention,aes(x = Tension_s, y = SR_water_VG,color = "SR"), size=1)+
  
  annotate("text", label = "DWP, fine sand", x = 25, y = 0.03,size=4,fontface="bold")+ 
  annotate("text", label = "CPCRW, silt loam", x = 75, y = 0.13,size=4,fontface="bold")+ 
  annotate("text", label = "SR, silty clay loam", x = 55, y = 0.3,size=4,fontface="bold")+ 
  
  labs (y = expression (bold ("volumetric moisture content")),
        x = expression (bold ("tension, kPa" )))+
  ylim(0,0.6)+
  theme_bw()+
  theme_kp()+
  theme (legend.position = "none")

```

---

# WSOC tables  
## soils
mg/g soil
```{r wsoc_soil, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="wsoc pore"}
wsoc_soil %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(Site),
                val = paste(wsoc_dunnett)) %>% 
  dplyr::select(Treatment,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
  
```

## pores
mg/L
```{r wsoc_pore, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="wsoc pore"}
wsoc_pore %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(Suction, Site),
                val = paste(wsoc_mgL)) %>% 
  dplyr::select(Treatment,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```


## pores
mg/g
```{r wsoc_pore, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="wsoc pore"}
wsoc_pore %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(Suction, Site),
                val = paste(wsoc_mgg)) %>% 
  dplyr::select(Treatment,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

---

# FTICR Pores -- figures
## native SOM
```{r vk_baseline, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Van Krevelen plot for TZSat pores",fig.width=10, fig.height=7,,fig.path = "images/"}

gg_vankrev(pore_long[pore_long$treatment=="time zero saturation",], aes(x=OC,y=HC, color=site))+
  scale_color_brewer(palette = "Set1")+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```

## treatment effect -- all peaks
```{r vk_treatments, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Van Krevelen plot for treatments",fig.width=10, fig.height=7,,fig.path = "images/"}
pore_long %>% 
  dplyr::mutate(treatment = factor(treatment, 
                                   levels = c("time zero saturation","field moist","drought","saturation")))->
           pore_long


gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  scale_color_brewer(palette = "Dark2")+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```

## treatment effect -- unique peaks
unique in each treatment compared to all, including TZsaturation
these are peaks that were uniquely **added** during a given treatment

```{r vk_unique, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Van Krevelen plot for unique peaks",fig.width=10, fig.height=7,fig.path = "images/"}
# set level of factors
pore_unique %>% 
  dplyr::mutate(unique = factor(unique, levels = c("field moist","drought","saturation")))->
           pore_unique

gg_vankrev(pore_unique,aes(x = OC, y = HC, color = unique))+
    scale_color_brewer(palette = "Dark2")+
facet_grid(tension~site)+
  
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```

## treatment effect -- relative abundance

```{r rel_abund, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Relative abundance",fig.width=9, fig.height=9,fig.path = "images/"}
# use file fticr_pore_relabundance_summary
# first, remove the `total` row
pore_relabund2 = pore_relabund[!pore_relabund$group=="total",]

# set Other as last factor
old.lvl = levels(factor(pore_relabund$Class))
pore_relabund$group = factor(pore_relabund$Class, 
                                            levels=c(sort(old.lvl[old.lvl!="Other"]), "Other"))

# set order of groups. all simple together and all complex together.

pore_relabund %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other")))->
           pore_relabund


ggplot(pore_relabund, aes(x = treatment, y = relabund2, fill = Class))+
  geom_bar(stat = "summary", width = 0.9)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_fill_viridis_d(option = "inferno")+
  
  xlab("")+
  ylab("% relative abundance")+
  
  facet_grid(tension~site)+
  
  theme_bw()+
  theme_kp()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## treatment effect -- NOSC

```{r NOSC_c, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="NOSC for CPCRW",fig.width=11, fig.height=18,fig.path = "images/"}
pore_nosc %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","drought","saturation")))->
  pore_nosc

#CPCRW
ggplot(pore_nosc[!pore_nosc$treatment=="baseline",], 
       aes(x = NOSC, fill = treatment, color = treatment))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  ylim(0,300)+

  facet_grid(site+tension~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()
```


## NOSC table
```{r NOSC, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="NOSC for SR",fig.width=11, fig.height=6,fig.path = "images/"}
pore_nosc %>% 
  group_by(tension,site,treatment) %>% 
  dplyr::summarise(median = median(NOSC))->
  pore_nosc_median

pore_nosc_median %>% 
  dplyr::mutate(sp = paste(treatment),
                val = round(median,4)) %>% 
  dplyr::select(tension,site,sp,val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```

## aromatic peaks
```{r aromatic, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="aromatic peaks", fig.width=12, fig.height=7,fig.path = "images/"}
pore_aromatic %>% 
  dplyr::mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","saturation","drought"))) ->
  pore_aromatic

## doing facet
ggplot(pore_aromatic[pore_aromatic$aromatic=="aromatic",], 
  aes(x = site, y = counts, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+ # fatten changes thickness of median line, lwd changes thickness of all lines
  geom_dotplot(binaxis = "y",position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  #scale_fill_viridis_d(option = "magma")+
  #scale_color_viridis_d(option = "magma")+

  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("aromatic peaks")+
  xlab("")+
  ylim(0,350)+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  facet_wrap(~tension)+
  
  theme_bw()+
  theme_kp()

```

## shannon diversity index --

```{r shannon, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="aromatic peaks", fig.width=12, fig.height=7,fig.path = "images/"}
pore_shannon %>% 
  dplyr::mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","saturation","drought"))) ->
  pore_shannon


ggplot(pore_shannon, aes(x = site, y = H, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+
  geom_dotplot(binaxis = "y", position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("Shannon Diversity Index")+
  xlab("")+
  #ylim(0,1)+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  facet_wrap(~tension)+
  
  theme_bw()+
  theme_kp()

```

# FTICR Pores -- tables
## peaks
```{r peaks, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="peaks 50 kPa"}
pore_peaks %>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other","total")))->
  pore_peaks

print("50 kPa")
pore_peaks %>% 
  ungroup %>% 
    filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

```{r peaks_1, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="peaks 1.5 kPa"}
print("1.5 kPa")
pore_peaks %>% 
  ungroup %>% 
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

## unique peaks
```{r uniquepeaks, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="peaks 50 kPa"}
pore_unique %>% 
  dplyr::select(Mass,tension,site,Class,unique) %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other"))) %>% 
  drop_na %>% 
  group_by(tension,site,Class,unique) %>% 
  dplyr::summarize(counts = n())->
  pore_unique_counts

print("50 kPa")
pore_unique_counts%>% 
  ungroup %>%
  filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

```{r uniquepeaks_1, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="peaks 50 kPa"}
print("1.5 kPa")
pore_unique_counts%>% 
  ungroup %>%
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

## relative abundance

```{r relabund_50, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="relabund 50 kPa"}
print("50 kPa")
pore_relabund%>% 
  ungroup %>% 
  filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

total = 100%

```{r relabund_1, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="relabund 1.5 kPa"}
print("1.5 kPa")
pore_relabund%>% 
  ungroup %>% 
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

total = 100%

---
---

# FTICR Soil -- figures 
## native SOM
```{r soil_vk_baseline, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Van Krevelen plot for baseline soil",fig.width=12, fig.height=5,fig.path = "images/"}

gg_vankrev(soil_long[soil_long$treatment=="baseline",],
       aes(x = OC, y = HC, color = site))+
  scale_color_brewer(palette = "Set1")+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```



## treatment effect -- all peaks
```{r soil_vk_treatments, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Van Krevelen plot for treatments",fig.width=12, fig.height=5,fig.path = "images/"}
soil_long %>% 
  dplyr::mutate(treatment = factor(treatment, 
                                   levels = c("baseline","time zero saturation","field moist","drought","saturation")))->
           soil_long

gg_vankrev(soil_long[soil_long$treatment=="field moist"|
                    soil_long$treatment=="drought"|
                     soil_long$treatment=="saturation",], # remove baselines 
         aes(x = OC, y = HC, color = treatment))+
  scale_color_brewer(palette = "Dark2")+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```

## treatment effect -- unique peaks
```{r soil_vk_unique, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Van Krevelen plot for unique peaks",fig.width=12, fig.height=5,fig.path = "images/"}
# set level of factors
soil_unique %>% 
  dplyr::mutate(unique = factor(unique, levels = c("field moist","drought","saturation")))->
           soil_unique

gg_vankrev(soil_unique,
         aes(x = OC, y = HC, color = unique))+
  scale_color_brewer(palette = "Dark2", na.translate=F)+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```



## treatment effect -- relative abundance
```{r soiL_rel_abund, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="Relative abundance",fig.width=9, fig.height=7,fig.path = "images/"}
# use file fticr_pore_relabundance_summary
# first, remove the `total` row

soil_relabund %>% 
  dplyr::filter(!Class=="total") %>% 
  mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed")))->
           soil_relabund


ggplot(soil_relabund, aes(x = treatment, y = relabund2, fill = Class))+
  geom_bar(stat = "summary", width = 0.9)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_fill_viridis_d(option = "inferno")+
  
  xlab("")+
  ylab("% relative abundance")+
  
  facet_grid(~site)+
  
  theme_bw()+
  theme_kp()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## NOSC
```{r soil_NOSC_c, echo=FALSE, fig.cap="NOSC for CPCRW", fig.height=6, fig.width=11, message=FALSE, warning=FALSE,fig.path = "images/"}
soil_nosc %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","drought","saturation")))->
  soil_nosc

ggplot(soil_nosc, 
       aes(x = NOSC, fill = treatment, color = treatment))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  ylim(0,1000)+

  facet_grid(site~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()
```

## NOSC table
```{r soilNOSC, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="NOSC for SR",fig.width=11, fig.height=6,fig.path = "images/"}
soil_nosc %>% 
  group_by(site,treatment) %>% 
  dplyr::summarise(median = median(NOSC))->
  soil_nosc_median

soil_nosc_median %>% 
  dplyr::mutate(sp = paste(treatment),
                val = round(median,4)) %>% 
  dplyr::select(site,sp,val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```
---

## aromatic peaks
```{r soil_aromatic, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="aromatic peaks", fig.width=12, fig.height=7,fig.path = "images/"}
soil_aromatic %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","saturation","drought")))->
  soil_aromatic

ggplot(soil_aromatic[soil_aromatic$aromatic=="aromatic",], 
  aes(x = site, y = counts, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+ # fatten changes thickness of median line, lwd changes thickness of all lines
  geom_dotplot(binaxis = "y",position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  #scale_fill_viridis_d(option = "magma")+
  #scale_color_viridis_d(option = "magma")+

  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("aromatic peaks")+
  xlab("")+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  theme_bw()+
  theme_kp()

```


---

# FTICR Soil -- tables 
## relative abundance
```{r soil_relabund_table, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="relabund 50 kPa"}
soil_relabund%>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed"))) %>% 

  ungroup %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

## peaks
```{r soil_peaks, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="peaks 50 kPa"}
soil_peaks %>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed","total"))) %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```
## unique peaks
```{r soil_uniquepeaks, echo=FALSE, warning=FALSE,message=FALSE,fig.cap="peaks 50 kPa"}
old.lvl = levels(factor(soil_unique_peaks$Class))
soil_unique_peaks$Class = factor(soil_unique_peaks$Class, 
                                            levels=c(sort(old.lvl[old.lvl!="total"]), "total"))

soil_unique %>% 
  dplyr::select(Mass,site,Class,unique) %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed"))) %>% 
  drop_na %>% 
  group_by(site,Class,unique) %>% 
  dplyr::summarize(counts = n())->
  soil_unique_counts

soil_unique_counts%>% 
  ungroup %>%
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```


