---
title: "3soils_markdown"
author: "Kaizad Patel"
output: 
  github_document:
    html_preview: true
    toc: true
---

```{r}
knitr::opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,
                      collapse = TRUE,
                      comment = "#>",
                      fig.path = "images/md/")
```

This is the RMarkdown file for the 3Soils experiment. Tables and figures for molecular results.
For formatted tables, see the Word document titled `000-3soils_markdown_YYYYMMDD.docx`.

Run: `r Sys.Date()`


```{r setup}
source("code/0b-packages.R")

# input files
#   CHARAC
charac = read.csv(CHARACTERIZATION)# <- "processed/soil_characterization.csv"
pore = read.csv(PORE_DISTRIBUTION)# <- "processed/pore_distribution.csv"

# WSOC
wsoc_pore = read.csv(WSOC_PORE)# <- "processed/wsoc_pore_summary.csv"
wsoc_soil = read.csv(WSOC_SOIL)# <- "processed/wsoc_soils_summary.csv"

# FTICR -- longform files
soil_raw = read.csv(FTICR_SOIL_RAW_LONG)# <- "fticr/fticr_soil_raw_longform.csv"
soil_long = read.csv(FTICR_SOIL_LONG)# <- "fticr/fticr_soil_longform.csv"
pore_long = read.csv(FTICR_PORE_LONG)# <- "fticr/fticr_pore_longform.csv"
pore_raw = read.csv(FTICR_PORE_RAW_LONG)# <- "fticr/fticr_pore_raw_longform.csv"

# FTICR -- relative abundance files
pore_relabund = read.csv(FTICR_PORE_RELABUND)# <- "fticr/fticr_pore_relabundance_groups2_hsd.csv"
soil_relabund = read.csv(FTICR_SOIL_RELABUND)# <- "fticr/fticr_soil_relabundance_hsd.csv"

# FTICR -- peaks files
pore_unique = read.csv(FTICR_PORE_UNIQUE)# <- "fticr/fticr_pore_uniquemolecules.csv"
soil_unique = read.csv(FTICR_SOIL_UNIQUE)# <- "fticr/fticr_soil_uniquemolecules.csv" 

pore_peaks = read.csv(FTICR_PORE_PEAKS)# <- "fticr/fticr_pore_peakscount.csv"
soil_peaks = read.csv(FTICR_SOIL_PEAKS)# <- "fticr/fticr_soil_peakscount.csv"


# FTICR_PORE
pore_aromatic = read.csv(FTICR_PORE_AROMATIC)# <- "fticr/fticr_pore_aromatic_counts.csv"
pore_meta = read.csv(FTICR_PORE_META)# <- "fticr/fticr_pore_meta.csv"
pore_long = read.csv(FTICR_PORE_LONG)# <- "fticr/fticr_pore_longform.csv"
pore_unique_peaks = read.csv(FTICR_PORE_UNIQUE_PEAKS)# <- "fticr/fticr_pore_unique_peakscount.csv"
pore_hcoc = read.csv(FTICR_PORE_HCOC)# <- "fticr/fticr_pore_hcoc.csv"
pore_nosc = read.csv(FTICR_PORE_NOSC)# <- "fticr/fticr_pore_nosc.csv"
pore_shannon = read.csv(FTICR_PORE_DIVERSITY)# <- "fticr/fticr_pore_shannondiversity.csv"

pore_shannon_summary = read.csv("fticr/pore_diversity_summary.csv")
soil_shannon_summary = read.csv("fticr/soil_diversity_summary.csv")

  
  
#FTICR_SOIL
soil_aromatic = read.csv(FTICR_SOIL_AROMATIC)# <- "fticr/fticr_soil_aromatic_counts.csv"
soil_nosc = read.csv(FTICR_SOIL_NOSC)# <- "fticr/fticr_soil_nosc.csv"
soil_hcoc = read.csv(FTICR_SOIL_HCOC)# <- "fticr/fticr_soil_hcoc.csv"
soil_unique_peaks = read.csv(FTICR_SOIL_UNIQUE_PEAKS)# <- "fticr/fticr_soil_unique_peakscount.csv"


# RESPIRATION
flux_data = read.csv(FLUX_DATA)
flux_summary = read.csv(FLUX_SUMMARY)
```
# Soil characterization
## summary table
```{r charac}
charac %>% 
  dplyr::mutate(variable = factor(variable, levels = c("TC_perc", "TN_perc", "TOC_perc", "WSOC_mg_g",
                                                "Ca_meq100g", "Mg_meq100g",
                                                "pH", "EC_dS_m", 
                                                "Sand_perc", "Silt_perc", "Clay_perc"))) %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(site),
                val = paste(summary_hsd)) %>% 
  dplyr::select(variable,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

---

## pore distribution
```{r pores"}
pore %>% 
  separate(pore_size_um, sep = "-", into = c("pore_size_lower", "pore_size_upper")) %>% 
  mutate(pore_size_upper = as.numeric(pore_size_upper)) %>% 
  arrange(pore_size_upper) %>% 
 ggplot(aes(x = pore_size_upper, y=perc_freq,color = site))+
  geom_line(size = 1, aes(group = site))+
  scale_color_brewer(palette = "Set2")+
  #geom_density(adjust=0.5)+
  
  labs (y = expression (bold ("distribution, %"),
                        x = expression (bold ("pore size" ))))+
  theme_bw()+
  theme_kp()
```

```{r, eval = FALSE}
pore_size = read.csv("data/processed/pore_size_perc_freq2.csv")

pore_size_summary = 
  pore_size %>% 
# make new bins
  dplyr::mutate(bins_um = case_when(pore_size==0 ~ "<100",
                                    pore_size>0&pore_size<1000~as.character(pore_size+100),
                                    pore_size>=1000&pore_size<2000 ~ "1000-2000",
                                    pore_size>=2000&pore_size<3000 ~ "2000-3000",
                                    pore_size>=3000&pore_size<4000 ~ "3000-4000")) %>% 
  group_by(bins_um) %>% 
  dplyr::summarise(CPCRW = round(sum(cpcrw),2),
                   DWP = round(sum(dwp),2),
                   SR = round(sum(sr),2)) %>% 
  knitr::kable()

```

---

## water retention curves

```{r wrc, fig.width=5, fig.height=5}

water_retention = read_excel("data/water_retention.xlsx")

# van genuchten plots
ggplot()+
  geom_line(data = water_retention,aes(x = Tension_c, y = CPCRW_water_VG*100), color = "#950000", size=1)+
  geom_line(data = water_retention,aes(x = Tension_d, y = DWP_water_VG*100), color = "#e6ab00", size=1)+
  geom_line(data = water_retention,aes(x = Tension_s, y = SR_water_VG*100), color = "#008cff", size=1)+
  
  annotate("text", label = "Alaska \n (silt loam)", x = 30, y = 20,size=4)+ 
  annotate("text", label = "Florida \n (fine sand)", x = 15, y = 4, size=4)+ 
  annotate("text", label = "Washington \n(silty clay loam)", x = 40, y = 35,size=4)+ 
  
  labs (y = expression (bold ("moisture (% v/v)")),
        x = expression (bold ("tension, kPa" )))+
  ylim(0,60)+
  theme_bw()+
  theme_kp()+
  theme (legend.position = "none")

```

---

# WSOC tables  
## soils
mg/g soil
```{r wsoc_soil}
wsoc_soil %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(Site),
                val = paste(wsoc_dunnett)) %>% 
  dplyr::select(Treatment,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
  
```

## pores
mg/L
```{r wsoc_pore_mgL}
wsoc_pore %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(Suction, Site),
                val = paste(wsoc_mgL)) %>% 
  dplyr::select(Treatment,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

figure
```{r}
wsoc = read.csv("data/processed/wsoc_pores_longform.csv")

ggplot(wsoc, aes(y = as.numeric(wsoc_mg_L), x = Site, color = Treatment))+
geom_point(position = position_dodge(width =0.5))+
facet_wrap(~Suction)
```

---

# FTICR domains 

```{r vk_domains, fig.height=7,fig.width=7}
pore_long %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other")))->
           pore_long

gg_vankrev(pore_long, aes(x=OC,y=HC,color=Class))+
  scale_color_viridis_d(option = "inferno")+
  theme_kp()+  
#  geom_segment(x = 0.0, y = 0.8, xend = 1.2, yend = 0.8,color="black",linetype="longdash")+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))

```

domains with NOSC

```{r}
pore_meta = read.csv(FTICR_PORE_META)
gg_vankrev(pore_meta, aes(x=OC,y=HC,color=(NOSC)))+
  geom_point(alpha = 0.7)+
  scale_color_viridis(option = "plasma", direction = -1)+
  scale_color_gradient2()+  
  #theme_kp()+
  labs (color = "NOSC")

```


# FTICR Pores -- figures
## native SOM
```{r vk_baseline, fig.width=10, fig.height=7}

  gg_vankrev(pore_long[pore_long$treatment=="time zero saturation",], aes(x=OC,y=HC, color=site))+
  scale_color_brewer(palette = "Set1")+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

vk1 = 
  gg_vankrev(pore_long[pore_long$treatment=="time zero saturation",], aes(x=OC,y=HC, color=tension))+
  scale_color_brewer(palette = "Set1")+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```




## treatment effect -- all peaks
```{r vk_treatments, fig.width=10, fig.height=7}
pore_long %>% 
  dplyr::mutate(treatment = factor(treatment, 
                                   levels = c("time zero saturation","field moist","drought","flood")))->
           pore_long


vk2 = 
  gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  scale_color_brewer(palette = "Dark2")+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  #scale_color_viridis_d()+
  scale_color_manual(values = c("#35b779ff", "#fde725ff","#443a83ff"))+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  ggtitle("viridis #35b779ff, #fde725ff, #443a83ff")+
  theme_kp()

## gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
##   #scale_color_viridis_d(option = "cividis")+
##   scale_color_manual(values = c( "#6B4596FF","#F68F46FF", "#042333FF"))+
##   facet_grid(tension~site)+
##   guides(colour = guide_legend(override.aes = list(alpha = 1)))+
##   ggtitle("#6B4596FF,#F68F46FF, #042333FF")+
##   theme_bw()+
##   theme_kp()
## 
## gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
##   #scale_color_viridis_d(option = "cividis")+
##   scale_color_manual(values = c( "#f7cb44ff", "#cc6a70ff", "#403891ff"))+
##   facet_grid(tension~site)+
##   guides(colour = guide_legend(override.aes = list(alpha = 1)))+
##   ggtitle("#f7cb44ff, #cc6a70ff, #403891ff")+
##   theme_bw()+
##   theme_kp()
## 
## gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
##   #scale_color_viridis_d(option = "cividis")+
##   scale_color_manual(values = c( "#f7cb44ff", "#de7065ff", "#403891ff"))+
##   facet_grid(tension~site)+
##   guides(colour = guide_legend(override.aes = list(alpha = 1)))+
##   theme_bw()+
##   ggtitle("#f7cb44ff, #de7065ff, #403891ff")+
##   theme_kp()
## 

```


```{r, eval = FALSE}
library(patchwork)
combined = vk1/vk2 + plot_layout(heights = c(1,2))
save_plot("images/vankrev.png", combined ,base_height = 10, base_width = 9)

```


## treatment effect -- unique peaks
unique in each treatment compared to all, including TZsaturation
these are peaks that were uniquely **added** during a given treatment

```{r vk_unique, fig.width=10, fig.height=7}
# set level of factors
pore_unique %>% 
  dplyr::mutate(unique = factor(unique, levels = c("field moist","drought","flood")))->
           pore_unique

gg_vankrev(pore_unique,aes(x = OC, y = HC, color = unique))+
  #    scale_color_brewer(palette = "Dark2")+
  scale_color_manual(values = c("#35b779ff", "#fde725ff","#443a83ff"))+
  
  facet_grid(tension~site)+
  
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```

peaks lost and gained

```{r, fig.height=8}
pore_lost = 
  pore_unique %>% 
  gather(treatment,loss, drought2:flood2)

gg_vankrev(pore_lost,aes(x = OC, y = HC, color = loss))+
  scale_color_brewer(palette = "Dark2", na.translate = FALSE)+
  facet_grid(treatment+tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```


## treatment effect -- relative abundance

```{r rel_abund, fig.width=9, fig.height=9}
# use file fticr_pore_relabundance_summary
# first, remove the `total` row
pore_relabund2 = pore_relabund[!pore_relabund$group=="total",]

# set Other as last factor
old.lvl = levels(factor(pore_relabund$Class))
pore_relabund$group = factor(pore_relabund$Class, 
                                            levels=c(sort(old.lvl[old.lvl!="Other"]), "Other"))

# set order of groups. all simple together and all complex together.

pore_relabund %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other")))->
           pore_relabund


ggplot(pore_relabund, aes(x = treatment, y = relabund2, fill = Class))+
  geom_bar(stat = "summary", width = 0.9)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_fill_viridis_d(option = "inferno")+
  
  xlab("")+
  ylab("% relative abundance")+
  
  facet_grid(tension~site)+
  
  theme_bw()+
  theme_kp()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## treatment effect -- NOSC

```{r NOSC_c, fig.width=11, fig.height=18}
pore_nosc %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","drought","flood")))->
  pore_nosc

#CPCRW
ggplot(pore_nosc[!pore_nosc$treatment=="baseline",], 
       aes(x = NOSC, fill = treatment, color = treatment))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  ylim(0,300)+

  facet_grid(site+tension~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()
```


## NOSC table
```{r NOSC, fig.width=11, fig.height=6}
pore_nosc %>% 
  group_by(tension,site,treatment) %>% 
  dplyr::summarise(median = median(NOSC))->
  pore_nosc_median

pore_nosc_median %>% 
  dplyr::mutate(sp = paste(treatment),
                val = round(median,4)) %>% 
  dplyr::select(tension,site,sp,val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```

## aromatic peaks
```{r aromatic, fig.width=12, fig.height=7}
pore_aromatic %>% 
  dplyr::mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","flood","drought"))) ->
  pore_aromatic

## doing facet
ggplot(pore_aromatic[pore_aromatic$aromatic=="aromatic",], 
  aes(x = site, y = counts, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+ # fatten changes thickness of median line, lwd changes thickness of all lines
  geom_dotplot(binaxis = "y",position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  #scale_fill_viridis_d(option = "magma")+
  #scale_color_viridis_d(option = "magma")+

  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("aromatic peaks")+
  xlab("")+
 # ylim(0,350)+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  facet_wrap(~tension)+
  
  theme_bw()+
  theme_kp()

```


aromatic peaks -- Van Krevelen

```{r}
pore_aromatic_vk = 
  pore_long %>% 
  left_join(dplyr::select(pore_meta, Mass, AImod), by = "Mass") %>% 
  dplyr::mutate(aromatic = case_when(AImod>0.5 ~ "aromatic")) %>% 
  filter(!is.na(tension) & !is.na(site))

gg_vankrev(pore_aromatic_vk[pore_aromatic_vk$aromatic=="aromatic",], aes(x = OC, y = HC))+
#  geom_point(data = pore_aromatic_vk[pore_aromatic_vk$Class=="Lignin",], color = "red", alpha = 0.1)+
  facet_grid(site~tension)

gg_vankrev(pore_aromatic_vk[pore_aromatic_vk$Class=="Lignin",], aes(x = OC, y = HC))+
  #geom_point(data = pore_aromatic_vk[pore_aromatic_vk$Class=="lignin",], color = "red")+
  facet_grid(site~tension)


```

## shannon diversity index --

```{r shannon, fig.width=12, fig.height=7}
pore_shannon %>% 
  dplyr::mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","flood","drought"))) ->
  pore_shannon


ggplot(pore_shannon, aes(x = site, y = H, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+
  geom_dotplot(binaxis = "y", position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("Shannon Diversity Index")+
  xlab("")+
  #ylim(0,1)+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  facet_wrap(~tension)+
  
  theme_bw()+
  theme_kp()

```

# FTICR Pores -- tables
## peaks
```{r peaks}
pore_peaks %>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other","total")))->
  pore_peaks

print("50 kPa")
pore_peaks %>% 
  ungroup %>% 
    filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

```{r peaks_1}
print("1.5 kPa")
pore_peaks %>% 
  ungroup %>% 
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  filter(Class=="total") %>% 
  knitr::kable(align = "r")
```

## unique peaks
```{r uniquepeaks}
pore_unique %>% 
  dplyr::select(Mass,tension,site,Class,unique) %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other"))) %>% 
  drop_na %>% 
  group_by(tension,site,Class,unique) %>% 
  dplyr::summarize(counts = n())->
  pore_unique_counts

print("50 kPa")
pore_unique_counts%>% 
  ungroup %>%
  filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

```{r uniquepeaks_1}
print("1.5 kPa")
pore_unique_counts%>% 
  ungroup %>%
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

## relative abundance

```{r relabund_50}
print("50 kPa")
pore_relabund%>% 
  ungroup %>% 
  filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

total = 100%

```{r relabund_1}
print("1.5 kPa")
pore_relabund%>% 
  ungroup %>% 
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

total = 100%
## aromatic peaks
```{r}

# pore_aromatic_summary %>% 
# ungroup %>% 
# dplyr::mutate(counts = paste(counts_mean,dunnett),
#               var = paste(tension,site)) %>% 
# dplyr::select(treatment, var, counts) %>% 
# spread(var, counts) %>% 
# knitr::kable()
```

## Shannon diversity
```{r}
pore_shannon_summary %>% 
  dplyr::mutate(H = paste(round(H_mean,2), "\U00B1", round(H_se,2), dunnett),
                H = str_replace_all(H, "NA",""),  
                var = paste(tension, site)) %>%
  dplyr::select(treatment, var, H) %>% 
  spread(var, H) %>% 
  knitr::kable()
```

---

# FTICR Soil -- figures 
## native SOM
```{r soil_vk_baseline, fig.width=12, fig.height=5}

gg_vankrev(soil_long[soil_long$treatment=="baseline",],
       aes(x = OC, y = HC, color = site))+
  scale_color_brewer(palette = "Set1")+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```



## treatment effect -- all peaks
```{r soil_vk_treatments, fig.width=12, fig.height=5,}
soil_long %>% 
  dplyr::mutate(treatment = factor(treatment, 
                                   levels = c("baseline","time zero saturation","field moist","drought","flood")))->
           soil_long

gg_vankrev(soil_long[soil_long$treatment=="field moist"|
                    soil_long$treatment=="drought"|
                     soil_long$treatment=="flood",], # remove baselines 
         aes(x = OC, y = HC, color = treatment))+
  scale_color_brewer(palette = "Dark2")+
  facet_grid(~site, drop = TRUE)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```

## treatment effect -- unique peaks
```{r soil_vk_unique, fig.width=12, fig.height=5}
# set level of factors
soil_unique %>% 
  dplyr::mutate(unique = factor(unique, levels = c("field moist","drought","flood")))->
           soil_unique

gg_vankrev(soil_unique,
         aes(x = OC, y = HC, color = unique))+
  scale_color_brewer(palette = "Dark2", na.translate=F)+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```

peaks lost and gained

```{r, fig.height=9, fig.width=9}
soil_lost = 
  soil_unique %>% 
  gather(treatment,loss, drought2:flood2)

gg_vankrev(soil_lost,aes(x = OC, y = HC, color = loss))+
  scale_color_brewer(palette = "Dark2", na.translate = FALSE)+
  facet_grid(treatment~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```





## treatment effect -- relative abundance
```{r soiL_rel_abund, fig.width=9, fig.height=7}
# use file fticr_pore_relabundance_summary
# first, remove the `total` row

soil_relabund %>% 
  dplyr::filter(!Class=="total") %>% 
  mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed")))->
           soil_relabund


ggplot(soil_relabund, aes(x = treatment, y = relabund2, fill = Class))+
  geom_bar(stat = "summary", width = 0.9)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_fill_viridis_d(option = "inferno")+
  
  xlab("")+
  ylab("% relative abundance")+
  
  facet_grid(~site)+
  
  theme_bw()+
  theme_kp()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## NOSC
```{r soil_NOSC_c, fig.height=6, fig.width=11}
soil_nosc %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","drought","flood")))->
  soil_nosc

ggplot(soil_nosc, 
       aes(x = NOSC, fill = treatment, color = treatment))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  ylim(0,1000)+

  facet_grid(site~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()
```

## NOSC table
```{r soilNOSC, fig.width=11, fig.height=6}
soil_nosc %>% 
  group_by(site,treatment) %>% 
  dplyr::summarise(median = median(NOSC))->
  soil_nosc_median

soil_nosc_median %>% 
  dplyr::mutate(sp = paste(treatment),
                val = round(median,4)) %>% 
  dplyr::select(site,sp,val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```

## lost/gained NOSC

```{r, fig.height=9, fig.width=9}
gained = read.csv("fticr/fticr_pore_newmolecules.csv")

ggplot(gained, 
       aes(x = NOSC, fill = newmolecules, color = newmolecules))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  #ylim(0,1000)+

  facet_grid(site+tension~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()

ggplot(gained, 
       aes(y = NOSC, x = treatment, color = newmolecules))+
  geom_boxplot(position = position_dodge(), fill = "white", lwd = 1,fatten = 1)+ # fatten changes thickness of median line, lwd changes thickness of all lines
 # geom_dotplot(binaxis = "y",position = position_dodge(0.75),                stackdir = "center", dotsize = 0.1, color = "black")
  facet_grid(site~tension)
```

---

## aromatic peaks

```{r soil_aromatic, fig.width=12, fig.height=7}
soil_aromatic %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","flood","drought")))->
  soil_aromatic

ggplot(soil_aromatic[soil_aromatic$aromatic=="aromatic",], 
  aes(x = site, y = counts, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+ # fatten changes thickness of median line, lwd changes thickness of all lines
  geom_dotplot(binaxis = "y",position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  #scale_fill_viridis_d(option = "magma")+
  #scale_color_viridis_d(option = "magma")+

  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("aromatic peaks")+
  xlab("")+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  theme_bw()+
  theme_kp()

```


---

# FTICR Soil -- tables 
## relative abundance
```{r soil_relabund_table}
soil_relabund%>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed"))) %>% 

  ungroup %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

## peaks
```{r soil_peaks}
soil_peaks %>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed","total"))) %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```
## unique peaks
```{r soil_uniquepeaks}
old.lvl = levels(factor(soil_unique_peaks$Class))
soil_unique_peaks$Class = factor(soil_unique_peaks$Class, 
                                            levels=c(sort(old.lvl[old.lvl!="total"]), "total"))

soil_unique %>% 
  dplyr::select(Mass,site,Class,unique) %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed"))) %>% 
  drop_na %>% 
  group_by(site,Class,unique) %>% 
  dplyr::summarize(counts = n())->
  soil_unique_counts

soil_unique_counts%>% 
  ungroup %>%
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```




## aromatic peaks

```{r}
# soil_aromatic_summary %>% 
#   ungroup %>% 
#   dplyr::mutate(counts = paste(counts_mean,dunnett)) %>% 
#   dplyr::select(treatment, site, counts) %>% 
#   spread(site, counts) %>% 
#   knitr::kable()
```

## Shannon diversity
```{r}
soil_shannon_summary %>% 
  dplyr::mutate(H = paste(round(H_mean,2), "\U00B1", round(H_se,2), dunnett),
                H = str_replace_all(H, "NA","")) %>%
  dplyr::select(treatment, site, H) %>% 
  spread(site, H) %>% 
  knitr::kable()
```


# Respiration 
## figures
Time series of CO2 flux
```{r}
ggplot(flux_data, aes(y = CO2_flux_mgC_gSoil_hr, x = inctime_hours, color = Treatment))+
  geom_point()+
  facet_grid(Treatment~Site)
```

Flux by site/treatment
```{r}
ggplot(flux_data, aes(y = CO2_flux_mgC_gSoil_hr, x = Site, color = Treatment))+
  geom_point(position = position_dodge(width=0.5))
```

## flux summary table

```{r}
flux_summary_table = 
  flux_summary %>% 
  gather(variable, value,MEAN_CO2_FLUX_ugC_gSoil_hr:CUM_CO2_FLUX_mgC_gSoil) %>% 
  dplyr::mutate(var = paste(variable, Site)) %>% 
  dplyr::select(Treatment, var,value) %>% 
  spread(var, value) %>% 
  knitr::kable()
```
