---
title: "3Soils -- FTICR"
author: "Kaizad Patel"
output: github_document
---

This is the RMarkdown file for the FTICR results from the 3Soils experiment. 
Tables and figures for molecular results.

Run: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,
                      collapse = TRUE,
                      comment = "#>", 
                      fig.path = "images/markdown-fticr/"
                      )
```


```{r inputs, include=FALSE, echo=FALSE}
source("code/0b-packages.R")

# input files
# FTICR -- longform files
soil_raw = read.csv(FTICR_SOIL_RAW_LONG)# <- "fticr/fticr_soil_raw_longform.csv"
#soil_long = read.csv(FTICR_SOIL_LONG)# <- "fticr/fticr_soil_longform.csv"
pore_long = read.csv(FTICR_PORE_LONG)# <- "fticr/fticr_pore_longform.csv"
pore_raw = read.csv(FTICR_PORE_RAW_LONG)# <- "fticr/fticr_pore_raw_longform.csv"

# FTICR -- relative abundance files
pore_relabund = read.csv(FTICR_PORE_RELABUND)# <- "fticr/fticr_pore_relabundance_groups2_hsd.csv"
soil_relabund = read.csv(FTICR_SOIL_RELABUND)# <- "fticr/fticr_soil_relabundance_hsd.csv"

# FTICR -- peaks files
pore_unique = read.csv(FTICR_PORE_UNIQUE)# <- "fticr/fticr_pore_uniquemolecules.csv"
soil_unique = read.csv(FTICR_SOIL_UNIQUE)# <- "fticr/fticr_soil_uniquemolecules.csv" 

pore_peaks = read.csv(FTICR_PORE_PEAKS)# <- "fticr/fticr_pore_peakscount.csv"
soil_peaks = read.csv(FTICR_SOIL_PEAKS)# <- "fticr/fticr_soil_peakscount.csv"


# FTICR_PORE
pore_aromatic = read.csv(FTICR_PORE_AROMATIC)# <- "fticr/fticr_pore_aromatic_counts.csv"
pore_meta = read.csv(FTICR_PORE_META)# <- "fticr/fticr_pore_meta.csv"
pore_long = read.csv(FTICR_PORE_LONG)# <- "fticr/fticr_pore_longform.csv"
pore_unique_peaks = read.csv(FTICR_PORE_UNIQUE_PEAKS)# <- "fticr/fticr_pore_unique_peakscount.csv"
pore_hcoc = read.csv(FTICR_PORE_HCOC)# <- "fticr/fticr_pore_hcoc.csv"
pore_nosc = read.csv(FTICR_PORE_NOSC)# <- "fticr/fticr_pore_nosc.csv"
pore_shannon = read.csv(FTICR_PORE_DIVERSITY)# <- "fticr/fticr_pore_shannondiversity.csv"

pore_shannon_summary = read.csv("fticr/pore_diversity_summary.csv")
soil_shannon_summary = read.csv("fticr/soil_diversity_summary.csv")
  
#FTICR_SOIL
soil_aromatic = read.csv(FTICR_SOIL_AROMATIC)# <- "fticr/fticr_soil_aromatic_counts.csv"
soil_nosc = read.csv(FTICR_SOIL_NOSC)# <- "fticr/fticr_soil_nosc.csv"
soil_hcoc = read.csv(FTICR_SOIL_HCOC)# <- "fticr/fticr_soil_hcoc.csv"
soil_unique_peaks = read.csv(FTICR_SOIL_UNIQUE_PEAKS)# <- "fticr/fticr_soil_unique_peakscount.csv"

```

Color palette used:  
treatments == viridis  

|  |  |  |
|-----|-----|-----|
|field moist | #35b779ff| green |
|drought |#fde725ff | yellow |
|flood | #443a83ff | blue |
|baseline | black | black |

sites  

|  |  |  |
|-----|-----|-----|
|Alaska | #950000 | red |
|Florida |#e6ab00 | yellow |
|Washington | #008cff | blue |

---

# FTICR domains 

```{r vk_domains, fig.height=7,fig.width=12}
pore_long %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other")))->
           pore_long

gg_domains = 
  gg_vankrev(pore_long, aes(x=OC,y=HC,color=Class))+
  scale_color_viridis_d(option = "inferno")+
  theme_kp()+  
#  geom_segment(x = 0.0, y = 0.8, xend = 1.2, yend = 0.8,color="black",linetype="longdash")+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))


gg_nosc = 
  gg_vankrev(pore_meta, aes(x=OC,y=HC,color=(NOSC)))+
  #geom_point(alpha = 0.7)+
#  scale_color_gradient2()+  
  labs (color = "NOSC")+
  theme(legend.position = "right")+
  scale_color_viridis(option = "cividis", direction = -1, name = "NOSC") +
  theme_bw()+
  theme(legend.position = "top",
          legend.key=element_blank(),
          legend.text = element_text(size = 12),
          legend.key.size = unit(1.5, 'lines'),
          panel.border = element_rect(color="black",size=1.5, fill = NA),
          
          plot.title = element_text(hjust = 0.05, size = 14),
          axis.text = element_text(size = 14, color = "black"),
          axis.title = element_text(size = 14, face = "bold", color = "black"))

gg_domains+gg_nosc

```

# FTICR pores - PCA figures
```{r, fig.height=7,fig.width=12}
# pore_raw = read.csv(FTICR_PORE_RAW_LONG)# <- "fticr/fticr_pore_raw_longform.csv"

relabund_temp = 
  pore_raw %>% 
  group_by(tension,site, treatment,Class,core) %>% 
  dplyr::summarize(compounds = n()) %>% # sum all COUNTS for each Class
  # now calculate relative abundance for each Class for each core
  group_by(tension,site, treatment, core) %>% 
  dplyr::mutate(total = sum(compounds),
                relabund = (compounds/total)*100)


## fine pores 

pore_relabund_pca_fine=
  relabund_temp %>% 
  ungroup %>% 
  dplyr::select(core,tension, site, treatment, Class, relabund) %>% 
  #filter(treatment=="time zero saturation") %>% 
  filter(tension=="50 kPa") %>% 
  spread(Class, relabund) %>% 
  replace(.,is.na(.),0) 

pore_relabund_pca_num_fine = 
  pore_relabund_pca_fine %>% 
  dplyr::select(.,-(1:4))

pore_relabund_pca_grp_fine = 
  pore_relabund_pca_fine %>% 
  dplyr::select(.,(1:4)) %>% 
  dplyr::mutate(row = row_number())

pca_fine = prcomp(pore_relabund_pca_num_fine, scale. = T)
#summary(pca_fine)

# biplot
ggbp_fine = 
  ggbiplot(pca_fine, obs.scale = 1, var.scale = 1, 
         #groups = pore_relabund_pca_grp$treatment, ellipse = F, circle = F,
         var.axes = TRUE)+
  geom_point(size=4,stroke=1, aes(fill = pore_relabund_pca_grp_fine$treatment, 
                                  shape = pore_relabund_pca_grp_fine$site), color = "black"
             )+
  scale_shape_manual(values = c(21,22,24))+
  
  scale_fill_manual(values = c("#fde725ff", "#35b779ff", "#443a83ff", "grey70"))+
  ggtitle("50 kPa")+
  theme_kp()+
  theme(legend.position = "right",
        plot.title = element_text(hjust = 0.5, face="bold"))+
  guides(fill=guide_legend(override.aes=list(shape=21)))


## coarse pores

pore_relabund_pca_coarse=
  relabund_temp %>% 
  ungroup %>% 
  dplyr::select(core,tension, site, treatment, Class, relabund) %>% 
  #filter(treatment=="time zero saturation") %>% 
  filter(tension=="1.5 kPa") %>% 
  spread(Class, relabund) %>% 
  replace(.,is.na(.),0) 

pore_relabund_pca_num_coarse = 
  pore_relabund_pca_coarse %>% 
  dplyr::select(.,-(1:4))

pore_relabund_pca_grp_coarse = 
  pore_relabund_pca_coarse %>% 
  dplyr::select(.,(1:4)) %>% 
  dplyr::mutate(row = row_number())

pca_coarse = prcomp(pore_relabund_pca_num_coarse, scale. = T)
#summary(pca_coarse)

# biplot
ggbp_coarse = 
  ggbiplot(pca_coarse, obs.scale = 1, var.scale = 1, 
         groups = pore_relabund_pca_grp_coarse$treatment, ellipse = F, circle = F,
         var.axes = TRUE)+
  geom_point(size=4,stroke=1, aes(fill = pore_relabund_pca_grp_coarse$treatment, 
                                  shape = pore_relabund_pca_grp_coarse$site), color = "black"
             )+
  scale_shape_manual(values = c(21,22,24))+
  
  scale_fill_manual(values = c("#fde725ff", "#35b779ff", "#443a83ff", "grey70"))+
  ggtitle("1.5 kPa")+
  theme_kp()+
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, face="bold"))+
  guides(fill=guide_legend(override.aes=list(shape=21)))

# combined biplot
ggbp_coarse+ggbp_fine
```

# FTICR Pores -- figures

# unique peaks per site

```{r unique_site, fig.width=8, fig.height=5}
#pore_long = read.csv(FTICR_PORE_RAW_LONG)# <- "fticr/fticr_pore_longform.csv"
fticr_pore_meta = read.csv(FTICR_PORE_META)

unique_pore_temp = 
  pore_long %>% 
  #  filter(reps==5) %>% 
  group_by(Mass, tension, site,  treatment) %>% 
  dplyr::summarize(presence=1) %>% 
  filter(treatment=="time zero saturation") %>% 
  group_by(Mass,tension) %>% 
  dplyr::mutate(reps=sum(presence)) %>% 
  left_join(dplyr::select(fticr_pore_meta, Mass, HC, OC), by = "Mass")

unique_pore = 
  unique_pore_temp %>% 
  filter(reps==1)

common_pore = 
  unique_pore_temp %>% 
  filter(reps>1) 

gg_vankrev(unique_pore_temp[unique_pore_temp$reps==1,], aes(x = OC, y = HC, color = site))+
  scale_color_manual(values = c('#950000', '#e6ab00','#008cff' ))+
  facet_grid(.~tension)+
  theme_kp()+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))
```


## treatment effect -- all peaks
```{r vk_treatments, fig.width=10, fig.height=7}
pore_long %>% 
  dplyr::mutate(treatment = factor(treatment, 
                                   levels = c("time zero saturation","drought","field moist","flood")))->
           pore_long

label = tribble(
  ~site, ~treatment, ~label, ~HC,  ~OC, 
  "Alaska", "time zero saturation", "aliphatic", 2.2, 1.1,
  "Alaska", "time zero saturation", "unsaturated \n polyphenolic", 1.2, 1.1,
  "Alaska", "time zero saturation", "aromatic", 0.5, 1.1
)

vk1 =
  gg_vankrev(pore_long[pore_long$treatment=="time zero saturation",], aes(x=OC,y=HC, color=tension))+
  scale_color_brewer(palette = "Set1")+
  geom_text(data = label, aes(label = label), color = "black", size=3)+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

vk2 =
  gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  #scale_color_manual(values = c("#fde725ff", "#35b779ff","#443a83ff"))+
    scale_color_manual(values = c("#fde725ff", "#35b779ff", "#443a83ff"))+
facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```

```{r combined_treatments, fig.height=10, fig.width=9}
library(patchwork)
combined = vk1/vk2 + plot_layout(heights = c(1,2))
#  plot_annotation(tag_levels = 'A') & 
#  theme(plot.tag = element_text(size = 15, face = "bold"))

#save_plot("images/vankrev.png", combined ,base_height = 10, base_width = 9)
combined
```

**individual panels**

```{r vk_panels_tz, fig.height=7, fig.width=10}
vk1 + facet_grid(tension~site)
```

```{r vk_panels_sites, fig.height=7, fig.width=10}
pore_long %>% 
  filter(treatment !="time zero saturation") %>% 
  filter(site == "Alaska") %>% 
  gg_vankrev(aes(x=OC, y=HC, color=treatment))+
  labs(title = "site = Alaska
       ")+
  #scale_color_manual(values = c("#fde725ff", "#35b779ff","#443a83ff"))+
  scale_color_manual(values = c("#fde725ff", "#35b779ff", "#443a83ff"))+
  facet_grid(tension~treatment)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_kp()+
  theme(plot.title = element_text(face = "bold", size = 12, hjust = 0),
        legend.position = "none")

pore_long %>% 
  filter(treatment !="time zero saturation") %>% 
  filter(site == "Florida") %>% 
  gg_vankrev(aes(x=OC, y=HC, color=treatment))+
  labs(title = "site = Florida
       ")+
  #scale_color_manual(values = c("#fde725ff", "#35b779ff","#443a83ff"))+
  scale_color_manual(values = c("#fde725ff", "#35b779ff", "#443a83ff"))+
  facet_grid(tension~treatment)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_kp()+
  theme(plot.title = element_text(face = "bold", size = 12, hjust = 0),
        legend.position = "none")

pore_long %>% 
  filter(treatment !="time zero saturation") %>% 
  filter(site == "Washington") %>% 
  gg_vankrev(aes(x=OC, y=HC, color=treatment))+
  labs(title = "site = Washington
       ")+
  #scale_color_manual(values = c("#fde725ff", "#35b779ff","#443a83ff"))+
  scale_color_manual(values = c("#fde725ff", "#35b779ff", "#443a83ff"))+
  facet_grid(tension~treatment)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_kp()+
  theme(plot.title = element_text(face = "bold", size = 12, hjust = 0),
        legend.position = "none")

```


## treatment effect -- unique peaks
unique in each treatment compared to all, including TZflood
these are peaks that were uniquely **added** during a given treatment

```{r vk_unique, fig.width=10, fig.height=7}
# set level of factors
pore_unique %>% 
  dplyr::mutate(unique = factor(unique, levels = c("drought","field moist","flood"))) %>% 
  filter(!is.na(unique))->
           pore_unique2

gg_vankrev(pore_unique2,aes(x = OC, y = HC, color = unique))+
  scale_color_manual(values = c("#fde725ff", "#35b779ff","#443a83ff"))+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_kp()
```

peaks lost and gained

```{r vk_lossgain, fig.height=9}
pore_lost = 
  pore_unique %>% 
  gather(treatment,loss, drought2:flood2)

gg_vankrev(pore_lost,aes(x = OC, y = HC, color = loss))+
  scale_color_brewer(palette = "Dark2", na.translate = FALSE)+
  facet_grid(treatment+tension~site)+
  
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```


## treatment effect -- relative abundance

```{r rel_abund, fig.width=9, fig.height=9}
# use file fticr_pore_relabundance_summary
# first, remove the `total` row
pore_relabund2 = pore_relabund[!pore_relabund$group=="total",]

# set Other as last factor
old.lvl = levels(factor(pore_relabund$Class))
pore_relabund$group = factor(pore_relabund$Class, 
                                            levels=c(sort(old.lvl[old.lvl!="Other"]), "Other"))

# set order of groups. all simple together and all complex together.

pore_relabund %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other")))->
           pore_relabund


ggplot(pore_relabund, aes(x = treatment, y = relabund2, fill = Class))+
  geom_bar(stat = "summary", width = 0.9)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_fill_viridis_d(option = "inferno")+
  
  xlab("")+
  ylab("% relative abundance")+
  
  facet_grid(tension~site)+
  
  theme_bw()+
  theme_kp()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## treatment effect -- NOSC

```{r NOSC_c, fig.width=11, fig.height=18}
pore_nosc %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","drought","flood")))->
  pore_nosc

ggplot(pore_nosc[!pore_nosc$treatment=="baseline",], 
       aes(x = NOSC, fill = treatment, color = treatment))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  ylim(0,300)+

  facet_grid(site+tension~treatment)+ #facet with two variables
  
  theme_kp()
```


## NOSC table
```{r NOSC}
pore_nosc %>% 
  group_by(tension,site,treatment) %>% 
  dplyr::summarise(median = median(NOSC))->
  pore_nosc_median

pore_nosc_median %>% 
  dplyr::mutate(sp = paste(treatment),
                val = round(median,4)) %>% 
  dplyr::select(tension,site,sp,val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```

<details>
  <summary>aromatic vs. lignin</summary>
## aromatic peaks
not doing much with aromatic peaks, because it excludes many lignins and tannins that contain aromatic groups

```{r}
pore_aromatic_vk = 
  pore_long %>% 
  left_join(dplyr::select(pore_meta, Mass, AImod), by = "Mass") %>% 
  dplyr::mutate(aromatic = case_when(AImod>0.5 ~ "aromatic"))

gg_vankrev(pore_aromatic_vk[pore_aromatic_vk$aromatic=="aromatic",], aes(x = OC, y = HC))+
  geom_point(data = pore_aromatic_vk[pore_aromatic_vk$Class=="Lignin",], color = "red", alpha = 0.1)+
  facet_grid(site~tension, drop = TRUE)+
  theme_kp()

```

</details>

## shannon diversity index

```{r shannon, fig.width=12, fig.height=5}
pore_shannon %>% 
  dplyr::mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","flood","drought"))) ->
  pore_shannon


ggplot(pore_shannon, aes(x = site, y = H, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+
  geom_dotplot(binaxis = "y", position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("Shannon Diversity Index")+
  xlab("")+
  #ylim(0,1)+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  facet_wrap(~tension)+
  
  theme_bw()+
  theme_kp()

```


# FTICR Pores -- tables

<details>
  <summary>Detected peaks</summary>
## peaks
```{r peaks}
pore_peaks %>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other","total")))->
  pore_peaks

print("50 kPa")
pore_peaks %>% 
  ungroup %>% 
    filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

```{r peaks_1}
print("1.5 kPa")
pore_peaks %>% 
  ungroup %>% 
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

</details>


<details>
  <summary>Unique peaks</summary>
## unique peaks
```{r uniquepeaks}
pore_unique %>% 
  dplyr::select(Mass,tension,site,Class,unique) %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Other"))) %>% 
  drop_na %>% 
  group_by(tension,site,Class,unique) %>% 
  dplyr::summarize(counts = n())->
  pore_unique_counts

print("50 kPa")
pore_unique_counts%>% 
  ungroup %>%
  filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

```{r uniquepeaks_1}
print("1.5 kPa")
pore_unique_counts%>% 
  ungroup %>%
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

</details>


<details>
  <summary>Relative abundance</summary>
## relative abundance

```{r relabund_50}
print("50 kPa")
pore_relabund%>% 
  ungroup %>% 
  filter(tension=="50 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

total = 100%

```{r relabund_1}
print("1.5 kPa")
pore_relabund%>% 
  ungroup %>% 
  filter(tension=="1.5 kPa") %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

total = 100%

</details>

<details>
  <summary>Shannon diversity</summary>
## Shannon diversity
```{r}
pore_shannon_summary %>% 
  dplyr::mutate(H = paste(round(H_mean,2), "\U00B1", round(H_se,2), dunnett),
                H = str_replace_all(H, "NA",""),  
                var = paste(tension, site)) %>%
  dplyr::select(treatment, var, H) %>% 
  spread(var, H) %>% 
  knitr::kable()
```

</details>

---

---

# FTICR Soil -- figures 
```{r soil_vk_baseline, fig.width=12, fig.height=5, eval = FALSE}
## native SOM
gg_vankrev(soil_long[soil_long$treatment=="baseline",],
       aes(x = OC, y = HC, color = site))+
  scale_color_brewer(palette = "Set1")+
  facet_grid(~site, drop = TRUE)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```

```{r soil_vk_treatments, fig.width=12, fig.height=5, eval = FALSE}
## treatment effect -- all peaks
soil_long %>% 
  dplyr::mutate(treatment = factor(treatment, 
                                   levels = c("baseline","time zero saturation","field moist","drought","flood")))->
           soil_long

gg_vankrev(soil_long[soil_long$treatment=="field moist"|
                    soil_long$treatment=="drought"|
                     soil_long$treatment=="flood",], # remove baselines 
         aes(x = OC, y = HC, color = treatment))+
  scale_color_brewer(palette = "Dark2")+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()

```

## treatment effect -- unique peaks
```{r soil_vk_unique, fig.width=12, fig.height=5}
# set level of factors
soil_unique %>% 
  dplyr::mutate(unique = factor(unique, levels = c("field moist","drought","flood")))->
           soil_unique

gg_vankrev(soil_unique,
         aes(x = OC, y = HC, color = unique))+
  scale_color_brewer(palette = "Dark2", na.translate=F)+
  facet_grid(~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```

peaks lost and gained

```{r vk_soil_lossgain, fig.width=8, fig.height=9}
soil_lost = 
  soil_unique %>% 
  gather(treatment,loss, drought2:flood2)

gg_vankrev(soil_lost,aes(x = OC, y = HC, color = loss))+
    scale_color_brewer(palette = "Dark2", na.translate = FALSE)+
  facet_grid(treatment~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  theme_kp()
```


## treatment effect -- relative abundance
```{r soiL_rel_abund, fig.width=9, fig.height=7}
# use file fticr_pore_relabundance_summary
# first, remove the `total` row

soil_relabund %>% 
  dplyr::filter(!Class=="total") %>% 
  mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed")))->
           soil_relabund


ggplot(soil_relabund, aes(x = treatment, y = relabund2, fill = Class))+
  geom_bar(stat = "summary", width = 0.9)+
  #scale_fill_brewer(palette = "Dark2")+
  scale_fill_viridis_d(option = "inferno")+
  
  xlab("")+
  ylab("% relative abundance")+
  
  facet_grid(~site)+
  
  theme_bw()+
  theme_kp()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## NOSC
```{r soil_NOSC_c,  fig.height=6, fig.width=11}
soil_nosc %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","drought","flood")))->
  soil_nosc

ggplot(soil_nosc, 
       aes(x = NOSC, fill = treatment, color = treatment))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  ylim(0,1000)+

  facet_grid(site~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()
```

## NOSC table
```{r soilNOSC, fig.width=11, fig.height=6}
soil_nosc %>% 
  group_by(site,treatment) %>% 
  dplyr::summarise(median = median(NOSC))->
  soil_nosc_median

soil_nosc_median %>% 
  dplyr::mutate(sp = paste(treatment),
                val = round(median,4)) %>% 
  dplyr::select(site,sp,val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```

## lost/gained NOSC

```{r nosc_soil_lossgain, fig.width=8, fig.height=9}
gained = read.csv("fticr/fticr_pore_newmolecules.csv")

ggplot(gained, 
       aes(x = NOSC, fill = newmolecules, color = newmolecules))+
  geom_histogram(binwidth = 0.10, position = "identity", alpha = 0.2)+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  # scale_fill_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #  scale_color_manual(values = c("#666666","#1B9E77", "#D95F02", "#7570B3"))+
  #geom_histogram(data = subset(fticr_pore_nosc, site = "CPCRW" | treatment=="field moist"), fill = "red", alpha = 0.2)+

  xlim(-2.5, 2.5)+
  #ylim(0,1000)+

  facet_grid(site+tension~treatment)+ #facet with two variables
  
  theme_bw()+
  theme_kp()

# ggplot(gained, 
#        aes(y = NOSC, x = treatment, color = newmolecules))+
#   geom_boxplot(position = position_dodge(), fill = "white", lwd = 1,fatten = 1)+ 
#   # fatten changes thickness of median line, lwd changes thickness of all lines
#  # geom_dotplot(binaxis = "y",position = position_dodge(0.75), stackdir = "center", dotsize = 0.1, color = "black")
#   facet_grid(site~tension)
```

## aromatic peaks
```{r soil_aromatic, fig.width=12, fig.height=5}
soil_aromatic %>% 
  mutate(treatment = factor(treatment,
                            levels = c("baseline","time zero saturation", "field moist","flood","drought")))->
  soil_aromatic

ggplot(soil_aromatic[soil_aromatic$aromatic=="aromatic",], 
  aes(x = site, y = counts, color = treatment, fill = treatment))+
  geom_boxplot(position = "dodge", fill = "white", lwd = 1,fatten = 1)+ # fatten changes thickness of median line, lwd changes thickness of all lines
  geom_dotplot(binaxis = "y",position = position_dodge(0.75), 
               stackdir = "center", dotsize = 0.4, color = "black")+
  
  #scale_fill_viridis_d(option = "magma")+
  #scale_color_viridis_d(option = "magma")+

  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+

  ylab("aromatic peaks")+
  xlab("")+
  geom_vline(xintercept = 1.5)+
  geom_vline(xintercept = 2.5)+
  
  theme_bw()+
  theme_kp()

```

---

# FTICR Soil -- tables 

<details>
  <summary>Relative abundance</summary>
  
## relative abundance
```{r soil_relabund_table}
soil_relabund%>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed"))) %>% 

  ungroup %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(relativeabundance)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

</details>

<details>
  <summary>Detected peaks</summary>
  
## peaks
```{r soil_peaks}
soil_peaks %>% 
  dplyr::mutate(Class = factor(Class, levels =
                          c("AminoSugar","Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed","total"))) %>% 
  ungroup %>% 
  dplyr::mutate(sp = paste(treatment),
                val = paste(peaks_count)) %>% 
  dplyr::select(site, Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")
```

</details>


<details>
  <summary>unique peaks</summary>
  
## unique peaks
```{r soil_uniquepeaks}
old.lvl = levels(factor(soil_unique_peaks$Class))
soil_unique_peaks$Class = factor(soil_unique_peaks$Class, 
                                            levels=c(sort(old.lvl[old.lvl!="total"]), "total"))

soil_unique %>% 
  dplyr::select(Mass,site,Class,unique) %>% 
  dplyr::mutate(Class = factor(Class, levels = 
                          c("AminoSugar", "Carb","Lipid","Protein","UnsatHC",
                            "ConHC","Lignin","Tannin","Unnamed"))) %>% 
  drop_na %>% 
  group_by(site,Class,unique) %>% 
  dplyr::summarize(counts = n())->
  soil_unique_counts

soil_unique_counts%>% 
  ungroup %>%
  dplyr::mutate(sp = paste(unique),
                val = paste(counts)) %>% 
  dplyr::select(site,Class,sp, val) %>% 
  spread(sp, val) %>% 
  knitr::kable(align = "r")

```

</details>


```{r}
## aromatic peaks
# soil_aromatic_summary %>% 
#   ungroup %>% 
#   dplyr::mutate(counts = paste(counts_mean,dunnett)) %>% 
#   dplyr::select(treatment, site, counts) %>% 
#   spread(site, counts) %>% 
#   knitr::kable()
```

<details>
  <summary>Shannon diversity</summary>
  
## Shannon diversity
```{r}
soil_shannon_summary %>% 
  dplyr::mutate(H = paste(round(H_mean,2), "\U00B1", round(H_se,2), dunnett),
                H = str_replace_all(H, "NA","")) %>%
  dplyr::select(treatment, site, H) %>% 
  spread(site, H) %>% 
  knitr::kable()
```

</details>

---

---


<details>
  <summary>color palettes</summary>

# testing color palettes
```{r palettes, fig.width=10, fig.height=7}
gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  #scale_color_viridis_d()+
  scale_color_manual(values = c("#35b779ff", "#fde725ff","#443a83ff"))+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  ggtitle("viridis #35b779ff, #fde725ff, #443a83ff")+
  theme_kp()

gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  #scale_color_viridis_d(option = "cividis")+
  scale_color_manual(values = c( "#6B4596FF","#F68F46FF", "#042333FF"))+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  ggtitle("#6B4596FF,#F68F46FF, #042333FF")+
  theme_bw()+
  theme_kp()

gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  #scale_color_viridis_d(option = "cividis")+
  scale_color_manual(values = c( "#f7cb44ff", "#cc6a70ff", "#403891ff"))+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  ggtitle("#f7cb44ff, #cc6a70ff, #403891ff")+
  theme_bw()+
  theme_kp()

gg_vankrev(pore_long[!pore_long$treatment=="time zero saturation",], aes(x=OC, y=HC, color=treatment))+
  #scale_color_viridis_d(option = "cividis")+
  scale_color_manual(values = c( "#f7cb44ff", "#de7065ff", "#403891ff"))+
  facet_grid(tension~site)+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  theme_bw()+
  ggtitle("#f7cb44ff, #de7065ff, #403891ff")+
  theme_kp()

gg_vankrev(unique_pore_temp[unique_pore_temp$reps==1,], aes(x = OC, y = HC, color = site))+
  #scale_color_manual(values = c("#000003","#721581", "#F1605D"))+
  #scale_color_manual(values = c("#6B4596FF","#F68F46FF", "#042333FF"))+
  #scale_color_manual(values = c("#de7065ff", "#f7cb44ff",  "#403891ff"))+
  #scale_color_manual(values = c('#008cff', '#e6ab00', '#ff5700'))+
  scale_color_manual(values = c('#ff0000', '#e6ab00','#008cff' ))+
  facet_grid(.~tension)+
  theme_kp()+
  guides(colour = guide_legend(override.aes = list(alpha = 1)))+
  ggtitle("2: #ff0000, #e6ab00,#008cff")

```

</details>


---

---

<details>
  <summary>Session Info</summary>

Date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>
